### 2016-02-16 ch05-initvals/initial-values.tex
Clean up timing table

\begin{table}
  \centering
  \centering
  \caption{Observed timing of the different estimation steps.}
% \input{\thisDir/table2.tex}
\pgfplotstabletypeset[precision=2,zerofill=true]{
Q  NBW  method  tsmooth    tinit  tfinal
 6  36  \model{true}    nan     nan     0.197034 
 6  36  \model{exist}   nan     nan     0.159937 
 6  36  \model{trunc}   0.745073    0.0623485   0.163107 
 6  36  \model{RFIR}    6.79873     0.0774866   0.175263 
 6  48  \model{true}    nan     nan     0.209216 
 6  48  \model{exist}   nan     nan     0.206823 
 6  48  \model{trunc}   1.00383     0.0902347   0.208173 
 6  48  \model{RFIR}    6.18632     0.0910651   0.221194 
20  36  \model{true}    nan     nan     0.445936 
20  36  \model{exist}   nan     nan     0.429752 
20  36  \model{trunc}   4.83667     0.225876    0.454757 
20  36  \model{RFIR}    6.92575     0.253981    0.482431 
20  48  \model{true}    nan     nan     0.467081 
20  48  \model{exist}   nan     nan     0.457577 
20  48  \model{trunc}   6.59726     0.312937    0.461114 
20  48  \model{RFIR}    8.05168     0.312297    0.468905 
}
\label{tbl:init:timing}

\TODO{fix pgfplotstable formatting}
\end{table}

@@

The \gls{LPM} itself solves $N$ linear systems of small dimensions ($2N_W + 1$ equations and a few degrees of freedom, i.e. $n_{\theta} \leq 2 N_W + 1$), hence the overall runtime will be $\bigO{N \cdot N_W^3}$ since solving a linear regression problem with $C$ parameters and $D$ datapoints takes $\bigO{C^3  + D C^2}$ operations\footnote{See http://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression-operation}.
The truncation of the impulse response relies on linear regression which takes $\bigO{N}$ operations since only $3$ parameters are estimated during this step.
Overall, this means that the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$

>>>>

\begin{table}
  \centering
  \centering
  \caption{Observed timing of the different estimation steps.}
% \input{\thisDir/table2.tex}
\pgfplotstabletypeset[zerofill=true,string replace={nan}{},precision=0,relative*=0, %round to 1 ms
    columns/method/.style={string type,column type=l,column name={\textsc{Method}}},
    columns/Q/.style={column type=c,column name={$Q\axisunit{dB}$},zerofill=false},
    columns/NBW/.style={column type=c,column name={$N_{3\unit{dB}}$},zerofill=false},
    columns/tsmooth/.style={column type=r,column name={$t_{\mathrm{smooth}} \axisunit{ms}$},multiply by=1000},
    columns/tinit/.style={column type=r,column name={$t_{\mathrm{init}} \axisunit{ms}$},multiply by=1000},
    columns/tfinal/.style={column type=r,column name={$t_{\mathrm{final}} \axisunit{ms}$},multiply by=1000},
]{%
Q  NBW  method  tsmooth    tinit  tfinal
 6  36  \model{\trueSymbol}    nan     nan     0.197034 
 6  36  \model{exist}   nan     nan     0.159937 
 6  36  \model{trunc}   0.745073    0.0623485   0.163107 
 6  36  \model{RFIR}    6.79873     0.0774866   0.175263 
 6  48  \model{\trueSymbol}    nan     nan     0.209216 
 6  48  \model{exist}   nan     nan     0.206823 
 6  48  \model{trunc}   1.00383     0.0902347   0.208173 
 6  48  \model{RFIR}    6.18632     0.0910651   0.221194 
20  36  \model{\trueSymbol}    nan     nan     0.445936 
20  36  \model{exist}   nan     nan     0.429752 
20  36  \model{trunc}   4.83667     0.225876    0.454757 
20  36  \model{RFIR}    6.92575     0.253981    0.482431 
20  48  \model{\trueSymbol}    nan     nan     0.467081 
20  48  \model{exist}   nan     nan     0.457577 
20  48  \model{trunc}   6.59726     0.312937    0.461114 
20  48  \model{RFIR}    8.05168     0.312297    0.468905 
}
\label{tbl:init:timing}
\end{table}

@@

The \gls{LPM} itself solves $N$ linear systems of small dimensions ($2N_W + 1$ equations and a few degrees of freedom, i.e. $n_{\theta} \leq 2 N_W + 1$), hence the overall runtime will be $\bigO{N n_{\theta}^3}$ since solving a linear regression problem with $C$ parameters and $D$ data points takes $\bigO{C^3  + D C^2}$ operations\footnote{See http://math.stackexchange.com/questions/84495/computational-complexity-of-least-square-regression}.
The truncation of the impulse response relies on linear regression which takes $\bigO{N}$ operations since only $3$ parameters are estimated during this step.
Overall, this means that the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$

### 2016-02-16 ch05-initvals/styles.inc.tex
Clean up timing table

\pgfplotstableset{
	%zerofill=true,
	after row=[3pt],
	assign column name/.code={%
        \pgfkeyssetvalue{/pgfplots/table/column name}{\multicolumn{1}{c}{\multirow{2}{*}{#1}} }%
    },
	columns/method/.style={string type,column name={\shortstack{\textsc{Method}\\\phantom{0}}}}, 
	columns/contribution/.style={column name={\textsc{Contribution}}},
	columns/P000/.style={column type=r,column name={\shortstack[r]{\textsc{Min.}\\{$0\%$}}}},
	columns/P025/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$25\%$}}}},
	columns/P050/.style={column type=r,column name={\shortstack[r]{\textsc{Median}\\{$50\%$}}}},
	columns/P075/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$75\%$ }}}},
	columns/P100/.style={column type=r,column name={\shortstack[r]{\textsc{Max.}\\{$100\%$}}}},
	columns/contribution/.style={column name={\shortstack[r]{\textsc{Contribution}\\ \vphantom{0}}},
	postproc cell content/.append code={
            %\ifnum1=\pgfplotstablepartno
                \pgfkeysalso{@cell content/.add={}{\%}}%
            %\fi
        },
	},
	every head row/.style={before row=\toprule, after row={\\\midrule}},
    every last row/.style={after row=\bottomrule}
}

>>>>

\pgfplotstableset{%
	zerofill=true,
	after row=[3pt],
                  every head row/.style={before row=\toprule, after row={\\\midrule}},
                  every last row/.style={after row=\bottomrule}
	assign column name/.code={%
        \pgfkeyssetvalue{/pgfplots/table/column name}{\multicolumn{1}{c}{\multirow{2}{*}{#1}} }%
    },
	columns/method/.style={string type,column name={\shortstack{\textsc{Method}\\\phantom{0}}}},
	columns/P000/.style={column type=r,column name={\shortstack[r]{\textsc{Min.}\\{$0\%$}}}},
	columns/P025/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$25\%$}}}},
	columns/P050/.style={column type=r,column name={\shortstack[r]{\textsc{Median}\\{$50\%$}}}},
	columns/P075/.style={column type=r,column name={\shortstack[r]{\vphantom{?}\\\textsc{$75\%$ }}}},
	columns/P100/.style={column type=r,column name={\shortstack[r]{\textsc{Max.}\\{$100\%$}}}},
	columns/contribution/.style={column name={\shortstack[r]{\textsc{Contribution}\\ \vphantom{0}}},
                    	postproc cell content/.append code={\pgfkeysalso{@cell content/.add={}{\%}}},
	}
}
